Large squeezing in Bose-Einstein condensates with large numbers of atoms

### 2013-07-12 large_number_squeezing_with_atoms.tex
Fix another typo.

We take a different approach and solve Eq.~(\ref{eqTwoModeHamiltonian}) directly for two reasons. First, we want access to the number variances of each state, not just the variance of the number difference between the states. Second, Eq.~(\ref{eqJosephson}) has led to the common misconception that no squeezing can be generated in this system if $\chi_{aa}+\chi_{bb}-2\chi{ab}=0$, as the effects of the nonlinearities on $\Delta \omega$ are dismissed as an irrelevent detuning. This is only the case if a spin-echo pulse is used half way through the application of (\ref{eqTwoModeHamiltonian}) (which is the protocol used in most spin squeezing experiments) or extra detunings are added to (\ref{eqJosephson}). Directly solving the Hamiltonian (\ref{eqTwoModeHamiltonian}) makes this clearer.

>>>>

We take a different approach and solve Eq.~(\ref{eqTwoModeHamiltonian}) directly for two reasons. First, we want access to the number variances of each state, not just the variance of the number difference between the states. Second, Eq.~(\ref{eqJosephson}) has led to the common misconception that no squeezing can be generated in this system if $\chi_{aa}+\chi_{bb}-2\chi_{ab}=0$, as the effects of the nonlinearities on $\Delta \omega$ are dismissed as an irrelevent detuning. This is only the case if a spin-echo pulse is used half way through the application of (\ref{eqTwoModeHamiltonian}) (which is the protocol used in most spin squeezing experiments) or extra detunings are added to (\ref{eqJosephson}). Directly solving the Hamiltonian (\ref{eqTwoModeHamiltonian}) makes this clearer.
